\documentclass[9pt]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[usenames]{color}
\usepackage{ragged2e}
\usepackage{hyperref}


\leftmargin=0.25in
\oddsidemargin=0.25in
\textwidth=6.0in
\topmargin=-0.25in
\textheight=9.25in

\raggedright

 %m\pagenumbering{arabic}
\pagestyle{empty}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME

\newenvironment{changemargin}[2]{%
  \begin{list}{}{%
    \setlength{\topsep}{0pt}%
    \setlength{\leftmargin}{#1}%
    \setlength{\rightmargin}{#2}%
    \setlength{\listparindent}{\parindent}%
    \setlength{\itemindent}{\parindent}%
    \setlength{\parsep}{\parskip}%
  }%
  \item[]}{\end{list}
}

\newcommand{\lineover}{
  \begin{changemargin}{-0.05in}{-0.05in}
    \vspace*{-8pt}
    \hrulefill \\
    \vspace*{-2pt}
  \end{changemargin}
}

\newcommand{\header}[1]{
  \begin{changemargin}{-0.5in}{-0.5in}
    \scshape{#1}\\
    \lineover
  \end{changemargin}
}

\newcommand{\contact}[4]{
  \begin{changemargin}{-0.5in}{-0.5in}
    \begin{center}
      {\Large \scshape {#1}}\\ \smallskip
      {#2}\\ \smallskip
      {#3}\\ \smallskip
      {#4}\smallskip
    \end{center}
  \end{changemargin}
}

\newenvironment{body} {
  \vspace*{-16pt}
\begin{changemargin}{-0.25in}{-0.5in}
  }
{\end{changemargin}
}


\newcommand{\school}[4]{
  \textbf{#1} \hfill \emph{#2\\}
  #3\\
  #4\\
}

\newenvironment{BodyText} {
  \raggedleft
  \centering
  %\begin{it}{}
}
{%\end{it}
}


% END RESUME DEFINITIONS

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Name
\contact{George Lewis}
        {ghl227@gmail.com}
        {(203) 918-4859}
        {\url{https://spontaneoussymmetry.com}}
\smallskip

\begin{body}
  \vspace{14pt}
  \emph{\textbf{Summary:}}{} Data scientist and software engineer with a history and passion for developing and deploying accurate and effective statistical models, designing data pipelines, and developing solid tools. %%, and with proven experience in developing data pipelines and creating tools to automate data processing.


%%Data science and data engineering leader with a history and passion for developing data products, training accurate and effective statistical models, assembling data pipelines, and building tools to facilitate valid and repeatable data analyses.
\end{body}

\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Skills
\header{Skills}
\begin{body}
  \vspace{14pt}
  \emph{\textbf{Modeling:}}{} Linear and logistic regression, decision trees, bagging, boosting, neural networks, MCMC, likelihood-based inference. \\
  \emph{\textbf{Languages:}}{} Python, Java, SQL, Scala, Clojure, Cython, C++.  Limited experience with R, C. \\
  \smallskip
  \emph{\textbf{Tools:}}{} Scikit-Learn, Pandas, Scipy, Jupyter, Postgres, Redshift, BigQuery, Spark, Airflow, AWS, Weka, XGBoost, matplotlib, seaborn, Flask, Play, Ring.  Experience with Tensorflow, Theano, tidyverse, PyMC3.  \\
\end{body}

\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Experience
\header{Experience}

\begin{body}

  \vspace{14pt}

  \textbf{LendUp} \hfill \emph{2013 - 2017}\\
  Head of Risk and Analytics \\
  Principal Data Scientist
  \begin{itemize}

  %% 2013-03-01 00:00:00 |    621 |   149960
  %% 2015-10-01 00:00:00 | 105142 | 28642760
  %% 2017-11-01 00:00:00 | 112478 | 37921910

    \item Founded the Risk and Analytics Team, which later became the Data Science Team.  Designed and implemented the risk and underwriting program, growing the size of company's loan portfolio by a factor of 200 while decreasing loss rates and achieving unit profitability.  Led the team from seed round funding through series B. \\

    \item Designed, trained, deployed, and monitored statistical models using logistic regression, generalized additive models, decision trees, and random forests to evaluate the credit risk of all applicants and to identify and mitigate fraud. \\

    \item Grew the Data Science Team from 1 to 11 members. Established best practices for building statistical models, and developed techniques and tools for analytics and monitoring.  Enforced high software standards and helped to develop a culture of strong programming practices within the Data Science Team. \\

    \item Built production-quality software in Java, Python, and Clojure to implement our risk program, serve and score models statistical moels, and to ingest and process data in real time. \\

    \item Recruited and trained the original Data Engineering Team.  Worked with Data Engineering to build an ETL framework, jobs, and pipelines for supporting machine learning and analytics using Python, Scala, Airflow and Spark.  Developed tooling to enable streamlined model deployment for data scientists. \\
  \end{itemize}

        \medskip

        \textbf{ATLAS experiment} \hfill \emph{2008 - 2013}\\
        Graduate student at New York University \\
        Worked on the Large Hadron Collider (LHC) at the European Organization for Nuclear Research (CERN) \\
        \medskip

        \begin{itemize}

          %% HistFactory + RooStats
        \item Developed and maintained a statistical framework in C++ that implemented novel modeling techniques and was used extensively throughout a 3000 person collaboration.

          %% ttbar analysis
        \item Built sophisticated models using custom likelihood functions and used modern frequentist inference techniques to produce world accurate measurements of fundamental particle properties.

         %% PROOF + SFRAME + Grid
        \item Used parallel batch computing to analyze petabytes of data distributed worldwide across data centers.

         %%
        \item Wrote production C++ code to select interesting collisions of the 10 million created per second.
         
         %% Code clean-up
        \item Enforced coding standards, conventions, and best practices across a large C++ and Python code base.

        \item Recipient of National Science Foundation US LHC Graduate Student Support Award.

        \end{itemize}

\end{body}

\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
\header{Education}

\begin{body}
  \vspace{14pt}
  \textbf{Ph.D. in Experimental High Energy Particle Physics }{} \hfill \emph{2013}{} \\
  \emph{New York University}, New York, NY{} \\
  \medskip
  \textbf{B.A. in Physics and Mathematics} \hfill \emph{2007} \\
  \emph{Columbia University}, New York, NY\\
\end{body}


% Education
\header{Portfolio}

\begin{body}
  \vspace{14pt}
  For a sample of my work and code, please see: {\url{https://spontaneoussymmetry.com/work}}
\end{body}

\end{document}
